Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations

\hypersetup{
	colorlinks,
    linkcolor= black, % internal links
    citecolor= camel, % citations
    urlcolor= black % external links/urls
}

@@

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %Karlan2015, Bruhn2019
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Multimedia delivery}
TV shows
\begin{itemize_2pt}
	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \textcolor{camel}{(Bjorvatn et al., 2020)} and Egypt \textcolor{camel}{(Barsoum et al., 2018)}
	\item Differential random incentivization schemes
	\item[] $\rightarrow$ No impact on business knowledge and business entry 
	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)

@@

Text messages
\begin{itemize_2pt}
	\item Examples: 
	\begin{itemize_2pt}
		\item Heuristics-based business advice \textcolor{camel}{(Cole and Schoar, 2019)}
		\item Daily personalised inventory level recommendations \textcolor{camel}{(Acimovic et al., 2020)}
	\end{itemize_2pt}
	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
\end{itemize_2pt}
\end{frame}

@@

Alternative measures of business profits \textcolor{camel}{(de Mel et al., 2009)}
	\begin{itemize_2pt}
		\item 15-16 unannounced visits during one month
		\item Random assignment of profit measure, and accounting diaries, and recall span
	\end{itemize_2pt}

@@

Survey media and frequencies {(Garlick et al, 2019)}
\begin{itemize_2pt}
	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.

	\item Random assignment to different survey modes and frequencies
	\begin{enumerate_2pt}
		\item Monthly in-person
		\item Weekly in-person
		\item Weekly phone
	\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}
Technological aids \textcolor{camel}{(Fafchamps et al., 2012)}
	\begin{itemize_2pt}
	\item Random assignment to Personalized Digital Assistants (PDAs)
	\
	\item Potential channels of impact
	\begin{enumerate_2pt}
		\item More timely data entry
		\item Greater accuracy (especially by correct use of skip patterns)
		\item More and more complex consistency checks

@@

	\item Some more obvious constraints:
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Credit constraints} (e.g., Berge et al., 2015, Gin\'e and Iacovone, 2021)
		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
		\item \textcolor{bdf}{Gender norms and constraints}
	\end{itemize_2pt}

@@

Potential for heuristics and rules of thumb
\begin{itemize_2pt}
	\item Example: Heuristics-based business training program by \citet{Drexler2014}
	\item[] $\rightarrow$ Discussed under \hyperlink{Drexler_thumb}{\beamergotobutton{alternative approaches}}
	\item See also, \textcolor{camel}{Cole and Schoar (2019)} and \textcolor{camel}{Arra\'iz et al. (2019)}
\end{itemize_2pt}
\end{frame}

@@

Family commitments
\begin{itemize_2pt}
	\item \textcolor{bdf}{Unequal responsibilities for child care} (see, e.g., \textcolor{camel}{Delecourt and Fitzpatrick, 2021})
	\begin{itemize_2pt}
		\item Audit study with mystery shoppers among drug stores in Uganda
		\item Average gender profit gap of 60\%
		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
		\begin{itemize_2pt}
			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
			\item .. have \textcolor{bdf}{48\% lower profits}.
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Market segregation
\begin{itemize_2pt}
	\item Markets can be geographically (and socially) segregated, especially in residential areas
	\begin{itemize_2pt}
		\item Potential \textcolor{bdf}{demand constraints} (in the spirit of \textcolor{camel}{Hardy and Kagy, 2020}, for women in Ghana)
		\item (Scant work, but seems important.)
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

@@

Learning styles
\begin{itemize_2pt}
	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
	\begin{itemize_2pt}
		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})
		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
	\end{itemize_2pt}

@@

Evidence on aspirations in entrepreneurship
\begin{itemize_2pt}
	\item Descriptive evidence that micro entrepreneurs show \textcolor{bdf}{sizable growth aspirations} \citep{Dalton2018}
	\begin{itemize_2pt}
		\item Both short-term and long-term, for growth in size, labor, and sales
		\item Entrepreneurs update dynamically given new information
	\end{itemize_2pt}

@@

	\item \textcolor{camel}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
		\item Cash also increases aspirations, labor supply, expenditures, and sales
	\end{itemize_2pt}

@@

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}

>>>>

\hypersetup{
	colorlinks,
    linkcolor= black, % internal links
    citecolor= camel, % citations
    urlcolor= camel % external links/urls
}

@@

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %[citation]Karlan2015, Bruhn2019
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Multimedia delivery}
TV shows
\begin{itemize_2pt}
	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \citep{Bjorvatn2020} and Egypt \citep{Barsoum2018}
	\item Differential random incentivization schemes
	\item[] $\rightarrow$ No impact on business knowledge and business entry 
	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)

@@

Text messages
\begin{itemize_2pt}
	\item Examples: 
	\begin{itemize_2pt}
		\item Heuristics-based business advice \citep{Cole2018}
		\item Daily personalized inventory level recommendations \citep{Acimovic2020}
	\end{itemize_2pt}
	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
\end{itemize_2pt}
\end{frame}

@@

Alternative measures of business profits \citep{deMel2009}
	\begin{itemize_2pt}
		\item 15-16 unannounced visits during one month
		\item Random assignment of profit measure, and accounting diaries, and recall span
	\end{itemize_2pt}

@@

Survey media and frequencies \citep{Garlick2019}
\begin{itemize_2pt}
	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.
	\item Random assignment to different survey modes and frequencies
	\begin{enumerate_2pt}
		\item Monthly in-person
		\item Weekly in-person
		\item Weekly phone
	\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}
Technological aids \citep{Fafchamps2012}
	\begin{itemize_2pt}
	\item Random assignment to Personalized Digital Assistants (PDAs)
	\item Potential channels of impact
	\begin{enumerate_2pt}
		\item More timely data entry
		\item Greater accuracy (especially by correct use of skip patterns)
		\item More and more complex consistency checks

@@

	\item Some more obvious constraints:
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Credit constraints} \citep[e.g.,][]{Berge2015, Gine2021}%[citation] mcenzie
		\item \textcolor{bdf}{Education} and \textcolor{bdf}{literacy constraints}
		\item \textcolor{bdf}{Gender norms and constraints}
		%\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
	\end{itemize_2pt}

@@

Potential for heuristics and rules of thumb
\begin{itemize_2pt}
	\item Example: Heuristics-based business training program by \citet{Drexler2014}
	\item[] $\rightarrow$ Discussed under \hyperlink{Drexler_thumb}{\beamergotobutton{alternative approaches}}
	\item See also, \citet{Cole2018} and \citet{Arraiz2019}
\end{itemize_2pt}
\end{frame}

@@

Family commitments
\begin{itemize_2pt}
	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep[see, e.g.,][]{Delecourt2021}
	\begin{itemize_2pt}
		\item Audit study with mystery shoppers among drug stores in Uganda
		\item Average gender profit gap of 60\%
		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
		\begin{itemize_2pt}
			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
			\item .. have \textcolor{bdf}{48\% lower profits}.
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Market segregation
\begin{itemize_2pt}
	\item Markets can be geographically (and socially) segregated, especially in residential areas
	\begin{itemize_2pt}
		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][, for women in Ghana]{Hardy2020}
		\item (Scant work, but seems important.)
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

@@

Learning styles
\begin{itemize_2pt}
	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
	\begin{itemize_2pt}
		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
	\end{itemize_2pt}

@@

Evidence on aspirations in entrepreneurship
\begin{itemize_2pt}
	\item Descriptive evidence that \textcolor{bdf}{micro-entrepreneurs show sizable growth aspirations} \citep{Dalton2018}
	\begin{itemize_2pt}
		\item Both short-term and long-term, for growth in size, labor, and sales
		\item Entrepreneurs update dynamically given new information
	\end{itemize_2pt}

@@

	\item \href{https://www.poverty-action.org/study/impact-cash-transfers-aspirations-and-goal-setting-economic-outcomes-and-well-being}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
		\item Cash also increases aspirations, labor supply, expenditures, and sales
	\end{itemize_2pt}

@@

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citet[See also,][]{Galiani2018}
	\end{itemize_2pt}
